Scaling up the hyperparameter grid for Naomi

### 2023-03-22 src/dev_scale-grid/scale-grid.Rmd
Should be range not limits (creates missing points in plot)

plot +
  geom_point(
    data = data.frame(mvQuad::getNodes(gaussian_2d)) %>%
      mutate(weight = mvQuad::getWeights(gaussian_2d)),
    aes(x = X1, y = X2, size = weight),
    col = multi.utils::cbpalette()[2],
    inherit.aes = FALSE
  ) +
  scale_size_continuous(limits = c(1, 2))
```

>>>>

plot +
  geom_point(
    data = data.frame(mvQuad::getNodes(gaussian_2d)) %>%
      mutate(weight = mvQuad::getWeights(gaussian_2d)),
    aes(x = X1, y = X2, size = weight),
    col = multi.utils::cbpalette()[2],
    inherit.aes = FALSE
  ) +
  scale_size_continuous(range = c(1, 2))
```
